On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-01-03 pps-linear-bound/J220-AJC-review-reply-1.tex

\documentclass[a4paper,14pt]{article} %размер бумаги устанавливаем А4, шрифт 12пунктов
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel} %используем русский и английский языки с переносами
\usepackage{amssymb,amsfonts,amsmath,mathtext,enumerate,float,amsthm} %подключаем нужные пакеты расширений
\usepackage[unicode,colorlinks=true,citecolor=black,linkcolor=black]{hyperref}
%\usepackage[pdftex,unicode,colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{indentfirst} % включить отступ у первого абзаца
\usepackage[dvips]{graphicx} %хотим вставлять рисунки?
\graphicspath{{illustr/}}%путь к рисункам

\makeatletter
\renewcommand{\@biblabel}[1]{#1.} % Заменяем библиографию с квадратных скобок на точку:
\makeatother %Смысл этих трёх строчек мне непонятен, но поверим "Запискам дебианщика"

\usepackage{geometry} % Меняем поля страницы.
\geometry{left=2cm}% левое поле
\geometry{right=1cm}% правое поле
\geometry{top=2cm}% верхнее поле
\geometry{bottom=2cm}% нижнее поле

%\renewcommand{\theenumi}{\arabic{enumi}}% Меняем везде перечисления на цифра.цифра
%\renewcommand{\labelenumi}{\arabic{enumi}}% Меняем везде перечисления на цифра.цифра
%\renewcommand{\theenumii}{.\arabic{enumii}}% Меняем везде перечисления на цифра.цифра
%\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}.}% Меняем везде перечисления на цифра.цифра
%\renewcommand{\theenumiii}{.\arabic{enumiii}}% Меняем везде перечисления на цифра.цифра
%\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.}% Меняем везде перечисления на цифра.цифра

\sloppy

\renewcommand\normalsize{\fontsize{14}{25.2pt}\selectfont}

%\usepackage[backend=biber,style=gost-numeric,sorting=nyt]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}

\begin{document}

Dear Editor and Referees,

Thank you for your attention paid to the paper.
I've done my best to cover all the remarks and advices,
and the present document is a detaled description of the improvements done.

First of all, I'd like to say special thanks to Referee 2 for the advice
to better guide the reader through the long list of technical auxiliary results.
As it was recommended, I've performed a major revision:
the structure of the paper has been rearranged.
Section 2 has been splitted into 3 smaller sections;
moreover, each section of main part has been divided into subsections
(see last paragraphs of Introduction for detailed description).

Due to such a rearrangement, numbers of most Lemmas, Theorems etc. have been changed,
and many results have been permutted to fit the new structure.
Thus, it is rather impossible to mention the page and line numbers of every change that has been made,
as it had been requested by the Editor.
As a possible solution, I've published all the workflow at my GitHub:
\\
https://github.com/nickkolok/sct-statya/commits/master
\\
As far as I put all my work on the topic into the single repository,
I've marked the commits concerning this paper with ``[J220]''.

As for Review 1, I agree with all the remarks completely.
\begin{enumerate}
	\item
		> Lemma 2.4: the reference is Russian, you may write a proof of Lemma 2.4 here in English

		Done. Lemma 2.4 is now Lemma 3.4 and has a self-contained proof.

	\item

		> page 10, line 3: $c_j \rightarrow 2c_J$ or you may eliminate this line.

		I've preferred the first option, i.e. replacement $c_j \rightarrow 2c_J$
\end{enumerate}

As for Review 2, I agree with all the remarks completely, except one.

Medium remarks:

\begin{enumerate}
	\item
		> The statement that integral point sets have to be finite is only true if we assume a dimension of at least 2.

		Fixed. Page 1, line -7.

	\item

		> As the author’s recent preprint
		``On diameter bounds for planar integral point sets in semi-general position''
		is not very long and overlaps the content of the present paper,
		it might be a good idea to summarize both to a single paper.

		This this the only remark for which I have to write a rebuttal for,
		and the reason is pretty simple:
		the paper ``On diameter bounds for planar integral point sets in semi-general position''
		has already been sent to another journal.
		Thus, it seems to be impossible to include its content into the present paper.
		Moreover, if the referees insist, I can
		\textbf{
		try to split the present paper into two ones:
		}
		one about the lower bound and one about integral point sets with distance 1.
		The present paper looks rather long, and the requested proofs (see below)
		have made it even more longer.
		However, if the paper will be published as a single one, then I'll also be very glad.

	\item

		> Please translate the titles of the non-english reference, like [8] and [3],
		into english or provide a link where those papers can be accessed.

		The translation has been done.
		However, the numbers of references have been changed, because
		the Editor requested to put the references in alphabetical order of authors.

	\item

		> Please add a self-contained proof for Lemma 2.4 since not all readers, including me, can read the one in [3].

		Done. Lemma 2.4 is now Lemma 3.4 and has a self-contained proof.

	\item

		> Is Lemma 2.6 also from [3] or have an obvious proof? Same for Lemma 2.7.

		Lemma 2.6 is now Lemma 4.2 and has a self-contained proof.
		\\
		Lemma 2.7 is now Lemma 4.4 and has a self-contained proof.

	\item

		> Was the inequality $d(2, 123) \leq d(2, 21491)$ used in the proof of Proposition 2.8?

		Yes, it was.
		The comment has been added before the proposition (which is now Proposition 3.5).

	\item

		> Please add a proof for Proposition 2.12.

		Thank you ver much for this remark.
		I have to admit that the result is not formulated correctly.
		The edits affect Definition 2.2 (ex Defintion 2.11), Proposition 2.3 (ex Proposition 2.12) and Lemma 2.4 (ex Lemma 2.13).
		Proposition 2.3 now has a self-contained proof.

	\item

		> The “blow up” procedure needs an explanation – not everybody is an expert on this.

		Construction 5.10 now provides the explanation.

\end{enumerate}

Minor remarks have been implemented precisely as they had been written.
As for minor remark 3, a brief proof for the corresponding Proposition 3.6 has been added.

%\printbibliography

\end{document}

### 2020-01-04 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Review 2, medium remark 6
[J220] Thank referees in Acknowledgements
[J220] Proper umlaut for Erdos in Introduction

\section{Introduction}
Let $\mathbb{N}$ be the set of all positive integers and let $|M_1 M_2|$ denote the Euclidean distance
between points $M_1$ and $M_2$ in a finite-dimensional space $\mathbb{R}^m$
(and, more generally, let $|\Delta|$ denote the length of line segment $\Delta$).
An \textit{integral point set} in $m$-dimensional Euclidean space, $m>2$, is a point set $M$ such that all the distances between the
points of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
Erd\"os and Anning proved~\cite{anning1945integral,erdos1945integral} that every integral point set consists of a finite number of points.
Taking this into account, we denote the set of all integral point sets of $n$ points in $m$-dimensional Euclidean space by
$\mathfrak{M}(m,n)$ (using the notation in~\cite{our-vmmsh-2018-translit})
and denote the set of all integral point sets in $m$-dimensional Euclidean space by $\mathfrak{M}(m,\mathbb{N})$.
The symbol $\# M$ will be used for cardinality of $M$, that is the number of points in $M$ in our case.

@@

Based on the exact values of $d(2,n)$ for $ 3 \leq n\leq 122$ and the estimate $d(2,123)>10000$
\cite{kurz2008bounds}, we derive the following proposition.
\begin{proposition}
	\label{obs:4_leq_n_leq_21491}
	The inequality
	\begin{equation}
		d(2,n) \geq 3^{1/4}\cdot2^{-3/2} \cdot n
	\end{equation}
	holds for $4 \leq n \leq 21491$.
\end{proposition}

@@

\section{Acknowledgements}
The author thanks Dr. Prof. E.M. Semenov for the fruitful discussion and ideas,
A.S. Chervinskaia for the idea of using the term ``facher'' and proofreading,
and Dr. A.S. Usachev for proofreading.

>>>>

\section{Introduction}
Let $\mathbb{N}$ be the set of all positive integers and let $|M_1 M_2|$ denote the Euclidean distance
between points $M_1$ and $M_2$ in a finite-dimensional space $\mathbb{R}^m$
(and, more generally, let $|\Delta|$ denote the length of line segment $\Delta$).
An \textit{integral point set} in $m$-dimensional Euclidean space, $m>2$, is a point set $M$ such that all the distances between the
points of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
Erd{\H{o}}s and Anning proved~\cite{anning1945integral,erdos1945integral} that every integral point set consists of a finite number of points.
Taking this into account, we denote the set of all integral point sets of $n$ points in $m$-dimensional Euclidean space by
$\mathfrak{M}(m,n)$ (using the notation in~\cite{our-vmmsh-2018-translit})
and denote the set of all integral point sets in $m$-dimensional Euclidean space by $\mathfrak{M}(m,\mathbb{N})$.
The symbol $\# M$ will be used for cardinality of $M$, that is the number of points in $M$ in our case.

@@

It is clear that for $n>123$ we have $d(2,n) \geq d(2,123)$.
Based on the exact values of $d(2,n)$ for $ 3 \leq n\leq 122$ and the estimate $d(2,123)>10000$
\cite{kurz2008bounds}, we derive the following proposition.
\begin{proposition}
	\label{obs:4_leq_n_leq_21491}
	The inequality
	\begin{equation}
		d(2,n) \geq 3^{1/4}\cdot2^{-3/2} \cdot n
	\end{equation}
	holds for $4 \leq n \leq 21491$.
\end{proposition}

@@

\section{Acknowledgements}
The author thanks Dr. Prof. E.M. Semenov for the fruitful discussion and ideas,
A.S. Chervinskaia for the idea of using the term ``facher'' and proofreading,
and Dr. A.S. Usachev for proofreading.
Also the author would like to owe a special thanks to the anonymous referees
for their helpful comments and suggestions on the paper.
